---
title: "Ejemplo"
author: "Juan R Gonzalez"
date: "14 de diciembre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "")
```


## R Markdown

This is an R _**Markdown**_ document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>. Also visit [here](http://www.google.com).


![caption](https://www.thespruce.com/thmb/mUUcxCn7iuQmUuRlkdJkqTDHphM=/1000x1000/filters:no_upscale()/pansywonderfall-5894ddd15f9b5874ee2062d3.jpg)


Aritmetic mean is computed using:

$$ \sum_{i=1}^n x_i  \log(\frac{x}{x+1})   $$

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r summary_cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, fig.height=3, fig.width=3, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



## Including tables


```{r table}
library(knitr)
kable(table(CO2$Plant, CO2$Type), caption="Mi tabla")
```



## Including in-line code

Mi dataset tiene `r nrow(CO2)` filas
